---
title: "Homework 2: Manipulating data frames"
author: 
- Author1
date: "`r Sys.time()`"
output: html_notebook
---


Explore the mtcars dataset (which is already included in R). Copy the mtcars dataset into a new variable (called it myCars), so that if you mess up, you can start again very easily (by copying mtcars into myCars again).

### Step 1: What is the hp (hp stands for “horse power”)
```{r Step1, echo=TRUE}
# 1 What is the highest hp?

# 2 Which car has the highest hp?

```

### Step 2: Explore mpg (mpg stands for “miles per gallon”)
```{r Step2, echo=TRUE}
# 3 What is the highest mpg?
# 4 Which car has the highest mpg? 
# 5 Create a sorted dataframe, based on mpg
```

### Step 3: Which car has the "best" combination of mpg and hp? 

6) What logic did you use? Note: No code is needed here just write what you would do.

7) Which car?

### Step 4: Which car has "best"" car combination of mpg and hp, where mpg and hp must be given equal weight? Note: This requires code.
```{r Step4, echo=TRUE}

```

